OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-06-04 main.tex
Added benchmark info and HMM method.

@@

Unlike those, OneD corrects a single variable instead of the whole matrix.
It uses only the total number of contacts per bin and thus estimates the
model parameters much faster than previous explicit methods.
Figure\ref{fig:times} shows the running times of the different methods on
the samples described in Table~\ref{tab:samples}. The fastest method is
\textit{vanilla} and the slowest is \textit{lgf}, with an over 100-fold
span between the two.

OneD is the second fastest method and it always ran in less than 1 min in
the conditions of the benchmark. Interestingly, the running time of OneD
is much more homogeneous than that of the other methods. The reason is
that the size of the regression problem to be solved by the \texttt{mgcv}
package is always the same at fixed reslution.

>>>>

\subsection{Copy number correction}

Briefly, a hidden Markov model with emissions distributed as a Student's
$t$ variable is fitted on the corrected total amount of contacts per bin.
The model consists of 7 states that correspond to 1, 2, 3, 4, 5, 6 and 8
copies of the target, for a total of 3 emission parameters (a single
scaling parameter, a single standard deviation and a single degree of
freedom for all the states) and 21 transition parameters.

The model is fitted with the Baum-Welch algorithm \citep{baum1966} until
convergence, following the detail given by \cite{filion2010systematic}.
The Viterbi path is then computed and corresponds to the inferred copy
number of each bin ($c_i$).

A correction equal to the square root of the copy number is then applied
to the whole matrix. More specifically, each cell is updated to

\begin{equation*}
\hat{x}_{ij}^* = \frac{\hat{x}_{ij}}{\sqrt{c_ic_j}}.
\end{equation*}

@@

Unlike the other methods, OneD corrects a single variable instead of the
whole matrix. It uses only the total number of contacts per bin and thus
estimates the model parameters much faster than previous explicit methods.
We measured the running time of the different tools on a 3.3~GHz machine
with 62 GB~RAM, always using the default paramters. Figure\ref{fig:times}
shows the running times of the different methods on the samples described
in Table~\ref{tab:samples} at 100 kbp resolution. The fastest method is
\textit{vanilla} and the slowest is \textit{lgf}, with an over 100-fold
span between the two.

OneD is the second fastest method and it always ran in less than 1 min in
the conditions of the benchmark. In all cases, the memory footprint was
less than 300 MB. Interestingly, the running time of OneD is much more
homogeneous than that of the other methods. The reason is that the size of
the regression problem to be solved by the \texttt{mgcv} package is always
the same at fixed reslution.
